---
output: rmarkdown::github_document
---
```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, error=FALSE)
options(width=120)
```
# greynoise

Query 'GreyNoise Intelligence 'API'

## Description

Tools are provided to query the 'GreyNoise Intelligence 'API'.

GreyNoise has a web site but there's nothing there at the moment: <http://greynoise.io/>

## What's Inside The Tin

- `gn_list_tags`:	List GreyNoise Intelligence Tags
- `gn_query_by_ip`:	Query all tags associated with a given IP address
- `gn_query_by_tag`:	Query all IPs that have a given tag

The following functions are implemented:

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/greynoise")
```

## Usage

```{r}
library(greynoise)
library(tidyverse)

# current verison
packageVersion("greynoise")
```

### List tags

```{r}
gn_list_tags()
```

### Query by a specific tag

Let's look for who scans for DNS endpoints

```{r}
(dns <- gn_query_by_tag("DNS_SCANNER_HIGH"))

glimpse(dns)
```

### Query by IP

We'll use fie first 5 IP addresses found in the previous query results.

```{r}
(what_else <- map_df(dns$ip[1:5], gn_query_by_ip))

glimpse(what_else)
```
